\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{6829hw}
\input{macros.tex}

\begin{document}

\newcounter{listcount}
\newcounter{sublistcount}


\handout{PS5}{December 6, 2011}{Instructor: Prof. Nick Feamster}
{College of Computing, Georgia Tech}{Problem Set 5: Cryptography and Anonymity}

This problem set has three {\bf optional} questions, each with several
parts (plus a fourth fun activity).  Answer them as clearly and
concisely as possible.  You may discuss ideas with others in the class,
but your solutions and presentation must be your own.  Do not look at
anyone else's solutions or copy them from anywhere. (Please refer to the
Georgia Tech honor code, posted on the course Web site).

Turn in your writeup {\bf December 14, 2011} by 11:59pm.
{\em Please upload your solutions to T-Square.  Other forms of
  submission will not be accepted!}  We will be providing more
information about how to turn in your assignment as the due date
approaches.

\begin{enumerate}
\item {\bf Crypto Hacks (25 Points).} Alice and Bob are good friends.
  To save time, they agree to simply find one good pair of primes, $p$
  and $q$ and therefore use the same public modulus, $n = pq$.  To save
  confusion over who signed which message, they select different
  exponents $e_a$ and $e_b$.  Show that, in this system, it's possible
  to decrypt a message $M$ sent to both of them if $\gcd(e_a, e_b) =
  1$.  That is, given, 
\begin{eqnarray*}
C_a &=& M^{e_a} (mod n) \\
C_b &=& M^{e_b} (mod n) 
\end{eqnarray*}
an adversary can compute $M$.

\item {\bf Internet Transparency (40 Points).}  Various projects are now
  trying to monitor the availability of various Web sites, informations
  and services.  Two such systems are Herdict
  (\url{http://herdict.org/}), and Google's Transparency Report
  (\url{http://google.com/transparencyreport/traffic/}.  Herdict relies
  on manual reports of downtime and unavailability, whereas Google's
  transparency report uses anomalies in traffic volumes to discover
  reachability problems from various regions for a particular service.
\begin{itemize}
\item {\bf 10 points.} What are the possible sources of inaccuracy of
  each approach? How would you verify the accuracy of information
  reported from  each of these systems?
\item {\bf 30 points.} Design and build a simple system that takes reports from
  the Herdict Web site and automatically measures their reachability
  properties from a variety of different locations.  For this purpose,
  you may need access to a set of distributed servers.  The PlanetLab
  testbed (\url{http://planet-lab.org/}) is a good resource for this.  I
  can provide you an account if you need one.
\end{itemize}

\item {\bf Anonymity (35 Points).} Download and install Tor.  
\begin{itemize}
\item {\bf (15 Points).} Identify the locations of the various entry and
  exit nodes that you can use in Tor.  What is the distribution of entry
  and exit nodes across Internet service providers and countries?
  Provide a table of the top 10 countries and ISPs (autonomous systems)
  that host Tor entry and exit nodes.
\item {\bf (20 Points).} The Tor Metrics page has some interesting
  examples of statistics of Tor usage in different countries during
  times when countries attempted to block Tor.  For example, see
  \url{http://goo.gl/6Pcfn} for an example of when Iran blocked Tor.
  Find at least two other examples of cases where Tor appears to have
  been blocked in a country.  {\em Include a graph from the Tor metrics
    page and a description of what you think is going on.}  How would
  you have stopped these events?
\end{itemize}

\end{enumerate}


\end{document}
