%%%%%%%%%%%%%%%%% Set options

\newcommand{\settitle}{Project 4: Network Security}
\newcommand{\course}{COS432/ELE432}
\newcommand{\coursename}{Information Security}
\newcommand{\duedate}{Friday, December 16}
\newcommand{\checkpointduedate}{Wednesday, December 7}
\newcommand{\duetime}{6:00 PM}
\newcommand{\distdate}{November 28, 2016}
\newcommand{\semester}{Fall 2016}
\newcommand{\firstcheckpointpercent}{2\%}
\newcommand{\secondcheckpointpercent}{10\%}
\newcommand{\staffemail}{\textbf{}}
\newcommand{\svnrepo}{}

%%%%%%%%%%%%%%%%

\documentclass[letterpaper,12pt]{report}
\usepackage{fullpage}
\usepackage[protrusion=true,expansion=auto]{microtype}
\usepackage{color}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{mathptmx}
\usepackage{textcomp}
\usepackage{fancyvrb}
\usepackage{listings}
\usepackage{paralist}
\usepackage{url}
\usepackage[
  breaklinks=true,colorlinks=true,linkcolor=black,%
  citecolor=black,urlcolor=black,bookmarks=false,bookmarksopen=false,%
  pdfauthor={\course},%
  pdftitle={\settitle},%
  pdftex]{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{multicol}
\def\textsb#1{{\fontseries{sb}\selectfont #1}}
\usepackage{mdframed}
\usepackage{calc}
\usepackage{nameref}
\usepackage{enumitem}
\setcounter{secnumdepth}{3}

\newcommand{\problemsetdone}{\bigskip\hfill$\Box{}$}

\newcommand{\htitle}
{
     \noindent\parbox{\textwidth}
    {
        \course\hfill \distdate\newline
        \coursename\hfill 
        \settitle \vspace*{-.5ex}\newline
        \mbox{}\hrulefill\mbox{}
    }
    \vspace{8pt}
    \begin{center}{\Large\bf{\settitle}}\end{center}
}
\newcommand{\handout}
{
    \thispagestyle{empty}
    \markboth{}{}
    \pagestyle{plain}
    \htitle
}

\newcommand{\problemsetheader}
{
\setlength{\parindent}{0pt}

\medskip

This project is split into two parts, with the first checkpoint due on {\bf \checkpointduedate} at {\bf \duetime} and the second checkpoint due on {\bf \duedate} at {\bf \duetime}.
The first checkpoint is worth {\firstcheckpointpercent} of your total grade, and the second checkpoint is worth \secondcheckpointpercent.
We strongly recommend that you get started early.
%Each semester everyone will be given ONE late extension that allows you to turn in up to one checkpoint up to 24 hours after the due date.
%Extensions are not automatic.
%So, if you want to use your late extension, you MUST send an e-mail to {\staffemail} before the deadline.
%Late work will not be accepted after 24 hours past the due date.

\medskip

This is a group project; you SHOULD work in \textbf{teams of two} and if you are in teams of two, you MUST submit one project per team.
If two different sets of answers are submitted, the one with lower total grade will be accepted.
Please find a partner as soon as possible.
If you have trouble forming a team, post on Piazza's partner search forum.
%Note that Aircrack-ng Suite, one of the tools required for Checkpoint 2 may not be compatible with your hardware.
%Please read the \textbf{\hyperlink{cp2setup}{Checkpoint 2 Setup}} in advance. Build your teams such that at least one member of the team can run the required tools.

\medskip

The code and other answers your group submits must be entirely your own work, and you are bound by the Student Code.
You MAY consult with other students about the conceptualization of the project and the meaning of the questions, but you MUST NOT look at any part of someone else's solution or collaborate with anyone outside your group.
You MAY consult published references, provided that you appropriately cite them (e.g., with program comments), as you would in an academic paper.

\medskip

Solutions MUST be submitted electronically, following the filename and solution formats specified under the submission checklist given at the end of each checkpoint.

\medskip

\hrulefill

\medskip
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\handout
%\setlength{\parindent}{0pt}
\problemsetheader
\medskip
\noindent
\emph{``You can't defend. You can't prevent. The only thing you can do is detect and respond.''}

\begingroup\raggedleft
-- Bruce Schneier\\
\endgroup

\newpage

\section*{Introduction}

This project will introduce you to common network protocols, the basics behind analyzing network traces from both offensive and defensive perspectives, and several local network attacks.

\vspace{-6pt}
\subsection*{Objectives}
\begin{itemize}
\item Gain exposure to core network protocols and concepts.
\item Understand offensive techniques used to attack local network traffic.
\item Learn to apply manual and automated traffic analysis to detect security problems.
\end{itemize}

\section*{Guidelines}
\begin{itemize}
\item You SHOULD work in a group of 2.
\item Your answers may or may not be the same as your classmates'.
%\item All the necessary files to start the project are given under a folder called ``mp4'' in your SVN repository: \url{\svnrepo}
\item We generated files for you to submit your answers in.
You MUST submit your answers in the provided files; we will only grade what's there!
\item Each submission file contains an example of expected format. Failure to follow this format may result in 1 point deduction for the section. You MAY delete the examples; they will be ignored (along with any other line starting with \#) when grading.
\end{itemize}

\section*{Required Tools}
\begin{itemize}
\item Wireshark 32 bit*
%\item Aircrack-ng Suite
%\item nmap
\item Python 2.7
\item dpkt (Python package)
\end{itemize}
* We strongly recommend using 32 bit version of Wireshark for Checkpoint 1.
Bugs within 64 bit version may prevent you from completing the task.

\newpage

%\subsection*{Read this First}

%This project asks you to perform attacks, with our permission, against a target network that we are providing for this purpose.
%Attempting the same kinds of attacks against other networks without authorization is prohibited by law and university policies and may result in \emph{fines, expulsion, and jail time}.
%\textbf{You MUST NOT attack any network without authorization!}
%There are also severe legal consequences for unauthorized interception of network data under the Electronic Communications Privacy Act and other statutes.
%Per the course ethics policy, you are required to respect the privacy and property rights of others at all times, \emph{or else you will fail the course.}
%See ``Ethics, Law, and University Policies'' on the course website.

\newpage

%Set counter for MP number
\setcounter{chapter}{4}

\input{proj4.1}

\newpage

\input{proj4.2}

\end{document}
