\documentclass[11pt]{article}

\usepackage{epsf}
\usepackage{epsfig}
\usepackage{url}
\usepackage{6829hw}
\input{macros.tex}

\begin{document}

\newcounter{listcount}
\newcounter{sublistcount}


\handout{H1}{August 23, 2011}{Instructor: Prof. Nick Feamster}
{College of Computing, Georgia Tech}{Problem Set 1: Case Study Research}

%This problem set has three questions, each with several parts.  Answer
%them as clearly and concisely as possible.  You may discuss ideas with
%others in the class, but your solutions and presentation must be your
%own.  Do not look at anyone else's solutions or copy them from
%anywhere. (Please refer to the Georgia Tech honor code, posted on the
%course Web site).

You should complete this problem set in a group of no more than five
students.  Please sign up on the wiki under a topic that interests you;
list your name as well as your email address so that your other group
members can contact you.

Turn in your writeup and talk on {\bf September 20, 2011} by 11:59pm.
{\em Please upload your solutions to T-Square.  Other forms of
  submission will not be accepted!}  We will be providing more
information about how to turn in your assignment as the due date
approaches.


\noindent
{\bf Information Security Case Study.}
Information security protection and failure has widely affected
today’s technology. This case-study research gives you a chance to
investigate one particular area of current relevance and impact and to
hear about other areas from your classmates.  With your group,
research the topic of your case study. Good starting points are Google
and Wikipedia; you will probably discover that the initial sources
that you discover will point you in some further directions. 

Let me know if you have trouble finding information, and I can help
you find some initial sources. In many cases, the opposite problem is
likely: you will probably find much more information than you can
reasonably cover in a class presentation. Your group should decide how
to handle large quantities of information. You could try to give an
overview of the entire area, or you could instead choose something
specific within the area and focus your research on the specific sub-
topic or incident.

Your group should prepare:
\begin{itemize}
\itemsep=-1pt
\item a 15-minute presentation that you will give
to the rest of the class, and
\item a two-page writeup summarizing your findings. 
\end{itemize}
Your goal should be to inform your classmates about the particular case
study that your group researched. There are a number of good
presentation programs available: Microsoft Powerpoint, OpenOffice
Presenter, Apple Keynote, Slidetex, and others. Fifteen minutes is not
long, so I would expect your group to base your talk on about three to
five sources. Additional sources can help you understand the area, but
you may not be able to fit them into your talk.

{\em I have provided initial topic assignments for on the wiki.  Please
sign up for a group by the end of this week, or I will place you in a
group.}  If a group of you wants to present on a different topic than
one of those listed on the wiki, you are welcome to do so, if you
consult me first.

Although you are expected to use outside sources for information, you:
\begin{itemize}
\itemsep=-1pt
\item must not copy-and-paste text or figures from those sources, and
\item must cite the sources. A citation should provide sufficient
  information for myself or anyone else to find the source that you
  used.
\end{itemize}

If you are unsure whether or not you are using outside material
appropriately, please ask me rather than guessing.

\end{document}
